---
title       : Iris Classification
subtitle    : Developing Data Product
author      : Becky Mak
job         : DDP
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Motivation

One of the hottest data science problem is __classification__.

To predict the species of Iris flower, a classification tree model is developed.

And users can input their observation, the apps will return the species.

--- .class #id 

## Data Summary
Here is the summary of data used to train the model
```{r}
data(iris)
d2=iris
species=levels(d2$Species)
summary(d2)
```

--- 

## Classification tree
We use the classification tree to build the model from package `rpart`.

```{r}
library(rpart)
fit = rpart(Species~., method="class", data=d2)
plot(fit, uniform=TRUE, main="Classification Tree for Iris")
text(fit, use.n=TRUE, all=TRUE, cex=.4)
```

--- 

## Example
When the user input the value (1,5,2,3), the outcome of the following will shown:

```{r}
input = data.frame(1,5,2,3)
names(input)= c("Sepal.Length","Sepal.Width","Petal.Length","Petal.Width")

pred = predict(fit, input)
predName = species[which.max(pred)]
```

The outcome will be `r predName`.
 